Statistical Mechanics Informed Neural Networks for Solar Wind modeling

### 2024-12-10 paper/main.tex
loss, paper

\begin{align*}
    r_x &\in \left[0, 230R_E\right] \\
    v_x &\in \left[0, 1000\right]\frac{km}{s} \\
    t &\in \left[0, 7200]s \\
\end{align*}

@@

\begin{align*}
    f_\alpha\left(r, v_{max}, t) &= 0 \\
    f_\alpha\left(r, v_{min}, t) &= 0 \\
    f_v\left(r_{min}, t) &= \mathbf{v}_{L1}(t) \\
    f_v\left(r_{max}, t) &= \mathbf{v}_{Earth}(t) \\
    f_E\left(r_{min}, t\right) &= E_{L1}(t) \\
    f_E\left(r_{max}, t\right) &= E_{Earth}(t) \\
    f_B\left(r_{min}, t\right) &= B_{L1}(t) \\
    f_B\left(r_{max}, t\right) &= B_{Earth}(t)
\end{align*}

@@

\section{Conclusion}
This work demonstrated the effectiveness of Physics-Informed Neural Networks to model Solar Wind's behavior tied to diverse statistical mechanics formulations that lead to Vlasov's kinetic model. By embedding the governing physical equations directly into the loss function, we can efficiently train a neural network to approximate the solution of this complex, non-linear system.

>>>>

\begin{align*}
    r_x &\in \left[0, 230R_E\right] \\
    v_x &\in \left[0, 1200\right]\frac{km}{s} \\
    t &\in \left[0, 7200]s \\
\end{align*}

@@

\begin{align*}
    f_\alpha\left(r, v_{max}, t) &= 0 \\
    f_\alpha\left(r, v_{min}, t) &= 0 \\
    f_\alpha\left(r, v, t_0) &= 0 \\
    f_E\left(r_0, t\right) &= E_{L1}(t) \\
    f_B\left(r_0, t\right) &= B_{L1}(t) \\
\end{align*}

@@

\subsection{3D-Simulations}

\section{Conclusion and future work}
This work demonstrated the effectiveness of Physics-Informed Neural Networks to model Solar Wind's behavior tied to diverse statistical mechanics formulations that lead to Vlasov's kinetic model. By embedding the governing physical equations directly into the loss function, we can efficiently train a neural network to approximate the solution of this complex, non-linear system.
